% !TEX root = template.tex

\section{Concluding Remarks}
\label{sec:conclusions}

In this project we evaluated, under one shared apparatus and a single-use test
protocol, whether adversarial (GRL) and contrastive (SupCon) training
objectives improve cross-environment WiFi CSI activity recognition over a
plain cross-entropy model. They do not: SupCon is worse by a bootstrap-resolved
margin; the GRL is worse still, with a much larger seed-to-seed spread; and
test-time adaptation is neutral at best. The deep CE model itself, however,
outperforms the SHARP-style shallow
network by $23.5$ accuracy points on the unseen environment --- on this
benchmark, backbone capacity mattered far more than any invariance objective.

The practical observation we consider most useful is \emph{why} the objectives
fail: frozen-encoder probes show that no domain attribute is linearly readable
from the learned features, so a domain adversary has nothing to remove. This
precondition is cheap to measure --- a linear probe on cached features ---
and we suggest checking it before investing in adversarial or contrastive
invariance on any dataset whose training split, like this one, is dominated by
a single environment. Benchmark designers, conversely, need several
well-populated training environments for domain-generalization claims to be
meaningful.

\subsection{Challenges and Lessons Learned}

Most of our effort went into making a negative result trustworthy: splits
frozen on day one and split by trace, normalization computed on train only, a
single logged test session with validation-selected checkpoints, and a
pre-registered row list. We learned to distrust single numbers twice. First,
the seed replicates showed a same-configuration swing on the GRL model larger
than some cross-configuration gaps, forcing us to report directions with
ranges rather than point estimates. Second, with 11 test traces even a
16-point accuracy gap is not resolved at the 95\% level by a trace-level
bootstrap --- the honest unit of analysis (the trace, not the thousands of
correlated windows) makes the dataset look much smaller than it appears. A
declared caveat also failed empirically: the classes invisible to validation
turned out to be the \emph{best} on test, a reminder that plausible
methodological worries should be tested, not just declared.

\subsection{Future Work}

With one held-out environment per rotation, this is a transfer study rather
than full domain generalization; the natural extension is a dataset with
several well-populated training environments and a complete leave-one-out over
all of them, where our diagnostic protocol transfers unchanged. On the
modeling side, the open question is whether \emph{any} training-time objective
can help when the domain factor is unreadable --- candidates that operate on
the input rather than the representation (stronger physics-informed
augmentations, synthetic environment simulation) are unaffected by our
structural argument.
