% !TEX root = template.tex

\section{Introduction}
\label{sec:introduction}

Wireless sensing turns the existing WiFi infrastructure into a device-free
perception system: a moving person perturbs the multipath propagation of the
radio signal, and these perturbations are recorded in the Channel State
Information (CSI) exposed by commodity network cards. Human Activity
Recognition (HAR) from CSI requires no wearable, no camera and no cooperation
from the subject, which makes it attractive for assisted living, surveillance
and smart-home applications~\cite{Wang-2019}. The micro-Doppler signature
derived from the CSI --- the distribution of reflected power over velocity and
time --- is among the most informative representations, and is the input we
work with throughout this report.

The obstacle that separates CSI HAR from deployment is not in-distribution
accuracy, which is by now high, but \emph{generalization across environments}.
A model trained in one room entangles the activity with the room's static
geometry (walls, furniture, transmitter--receiver placement); moved to a new
room, the same activity produces a different multipath fingerprint and accuracy
drops. The literature has responded with two families of representation-shaping
objectives: \emph{adversarial domain-invariance}, where a domain classifier
trained through a gradient reversal layer (GRL)~\cite{Ganin-2016} pushes the
encoder to discard environment-specific cues, and \emph{supervised contrastive}
(SupCon) learning~\cite{Khosla-2020}, which promises a more transferable
embedding geometry. Whether these objectives actually help on a given
benchmark is usually assumed rather than tested under controlled conditions.

In this work we test exactly that, on the SHARP dataset~\cite{Meneghello-2023}
under a leave-one-environment-out protocol: with backbone, data pipeline,
sampler, seed and evaluation harness held identical, does adding a GRL or
replacing cross-entropy (CE) with SupCon improve transfer to an unseen
environment? Our answer is a controlled negative result, together with an
explanation of why it had to be negative on this class of datasets.

\textbf{Contributions.} The key contributions of this paper are:
\begin{itemize}
\item A controlled comparison, under one shared experimental apparatus and a
single-use test protocol, of CE, CE+GRL and SupCon for cross-environment CSI
HAR, anchored to a faithful reproduction of the SHARP reference model. Our
deep CE model reaches macro-F1 $0.804$ on the held-out environment, against
$0.543$ for the SHARP-style shallow network in the identical recipe.
\item Evidence that neither objective improves over plain CE: SupCon loses
$7.8$ accuracy points (bootstrap-resolved) and the GRL loses $15.8$ with a
$10\times$ larger seed instability than CE.
\item An explanation via frozen-encoder diagnostics: no domain attribute is
linearly readable from the learned features, so the adversary has no target ---
a structural property of training splits dominated by a single environment,
replicated here across two rotations, two seeds and three loss families.
\item A statistical protocol suited to small LOEO test sets: trace-level paired
bootstrap, explicit separation of test-sampling and seed variance, and
declared multiplicity --- under which we also show test-time adaptation (T3A,
AdaBN) and amplitude augmentation do not close the gap.
\end{itemize}

The remainder of the paper is organized as follows. \secref{sec:related_work}
reviews related work. \secref{sec:processing_architecture} describes the
processing pipeline, \secref{sec:model} the dataset and features, and
\secref{sec:learning_framework} the learning framework and the evaluation
protocol. \secref{sec:results} presents the experimental results and
\secref{sec:conclusions} offers concluding remarks.
