% !TEX root = template.tex

\section{Processing Pipeline}
\label{sec:processing_architecture}

The system maps a raw CSI recording to an activity label through four stages,
shared identically by every configuration we compare: (i) a \emph{Doppler
front-end} that turns each antenna's CSI into a micro-Doppler time--velocity
map; (ii) a \emph{windowing} stage that segments each recording into
fixed-length windows and normalizes them with training-only statistics; (iii) a
shared convolutional \emph{encoder} mapping a window to a feature vector; and
(iv) a task \emph{head} producing per-window class scores, fused across the
four antennas into one prediction per window. The configurations differ
\emph{only} in the training objective attached to the encoder (plus, for the
adversarial ones, a domain head that exists at training time only): front-end,
windowing, encoder architecture, sampler, fusion and evaluation harness are
byte-for-byte the same. This single-apparatus design is what makes the
comparison a test of the loss family rather than of incidental engineering
differences.

\section{Signals and Features}
\label{sec:model}

\textbf{Dataset.} We use the SHARP micro-Doppler
dataset~\cite{Meneghello-2023}, collected with identical IEEE~802.11 hardware
in \emph{three environments} --- a bedroom, a living room and a laboratory ---
with three subjects performing eight activities (labelled C, E, H, J, L, R, S,
W; among them, E is the empty room, W walking, R running, J jumping and L
sitting). The recordings are organized into seven capture sets over twelve
campaigns; each physical recording (a \emph{trace}) is captured on four
antennas. The environment structure enables a leave-one-environment-out
evaluation; its imbalance --- the bedroom dominates the collection, and the
living room appears in a single capture set --- turns out to be central to our
findings (\secref{sec:results}).

\textbf{Pre-processing and features.} From each antenna's CSI we obtain the
micro-Doppler representation as in the reference pipeline, yielding a
time--velocity map per antenna. We deliberately did not re-engineer the
front-end: keeping it fixed isolates the variable under study, the training
objective. Because the velocity and time axes carry a physical orientation,
velocity flips and time reversal are excluded from augmentation.

\textbf{Windowing and normalization.} Each trace is segmented into fixed-length
windows with a fixed hop (a larger hop at evaluation time). Normalization
statistics $(\mu,\sigma)$ are computed on the training split only, per
rotation, stored in the frozen split file, and reused identically on validation
and test.

\textbf{Splits.} Two rules govern every split and are enforced by blocking
assertions in the code. First, \emph{we split by trace, never by window}: all
windows of a trace, on all four antennas, fall entirely on one side of the
train/val/test partition --- windows of the same trace on both sides would leak
the static channel and inflate every metric. Second, splits are frozen once as
JSON files under version control and never edited. The primary rotation holds
out the laboratory for test (11 traces); a second rotation holds out the living
room (15 traces) and is used for replication. Rare activity--environment cells
are pinned into training to guarantee coverage. One consequence is declared
up-front: the small validation split does not contain every class (no C, E, S
traces in the primary rotation), so validation macro-F1 is a 5-class,
within-run selection signal, not comparable to the 8-class test metric --- and
in \secref{sec:results} we test empirically whether this selection blindness
harmed the affected classes.

\section{Learning Framework}
\label{sec:learning_framework}

\textbf{Shared backbone.} All configurations except C0 share a deep residual
convolutional encoder~\cite{He-2016} ($\approx$2.8\,M parameters, feature
dimension $d_{\mathrm{enc}}=256$), chosen after a throughput gate on the target
hardware. C0 uses a faithful reimplementation of the shallow, wide SHARP
network~\cite{Meneghello-2023}, so the reproduction is architecturally honest;
the same network is also dropped into the exact C1 recipe as a backbone
ablation (\emph{C1-sharplike}), so that the backbone axis is isolated with
everything else held fixed.

\textbf{Configurations.} \tab{tab:configs} summarizes them. C0 is the
baseline (the prior approach); C1 is our model; C2--C4 are its objective
variants, spanning a $2\times2$ design over loss family (CE vs.\ SupCon) and
adversary (none vs.\ GRL):
\begin{itemize}
\item \textbf{C0} --- SHARP reproduction on the paper's 5-class core and split,
with the paper's antenna decision fusion.
\item \textbf{C1} --- CE with label smoothing on the shared backbone; our model,
and the internal control for C2--C4.
\item \textbf{C2} --- C1 plus a capture-set classifier trained through a
GRL~\cite{Ganin-2016}:
$\mathcal{L}=\mathcal{L}_{\mathrm{task}}+\beta\,\lambda(p)\,\mathcal{L}_{\mathrm{env}}$
with a fixed ramp $\lambda(p)$.
\item \textbf{C3} --- SupCon~\cite{Khosla-2020}: a contrastive phase trains
encoder and projection head with a $P{\times}K$ sampler and two augmented views
per sample; a frozen-encoder linear probe then selects and evaluates the
checkpoint. A CE fine-tune of the whole network from the SupCon initialization
(\emph{C3-ft}) gives the representation a fair shot beyond the frozen probe.
\item \textbf{C4} --- SupCon+GRL. \emph{Closed on evidence, not trained}: the
diagnostics of \secref{sec:res_diag} show no readable domain target under
either loss family, so C4 could only reproduce ``C3 plus noise''. We report
this as an evidence-based triage decision rather than spend its budget
confirming a foregone null.
\end{itemize}

\begin{table}[t]
\centering
\caption{Configurations. C0 is the prior-approach baseline, C1 our model,
C2--C4 its objective variants. All but C0 share one backbone, pipeline, sampler
and harness.}
\label{tab:configs}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{llll}
\hline
\textbf{Cfg} & \textbf{Loss} & \textbf{Adversary} & \textbf{Role} \\
\hline
C0 & CE (SHARP) & --- & baseline (prior approach) \\
C1 & CE         & --- & our model / CE control \\
C2 & CE         & GRL & adversarial invariance \\
C3 & SupCon     & --- & contrastive \\
C4 & SupCon     & GRL & closed on evidence \\
\hline
\end{tabular}}
\end{table}

\textbf{Sampler, optimization, reproducibility.} The contrastive configuration
uses a $P{\times}K$ sampler drawing $K$ distinct traces from each of $P$
classes per batch, with a minimum reuse offset so a batch never contains
near-duplicate windows of one trace; gradient accumulation is forbidden in the
contrastive phase, as it would corrupt the in-batch positive/negative
structure. A single seed (42) governs initialization, per-epoch sampler
reseeding and augmentation; seed-43 replicates of C1 and C2 measure the
training-variance floor. Differences within that floor are treated as
comparable, not as improvements.

\textbf{Evaluation harness and the single-use test rule.} One shared harness
maps a checkpoint to per-set metric files; C0's decision fusion is a thin
wrapper over the same harness. Checkpoint selection uses validation only, and
the \emph{test set is evaluated exactly once}, at the end, in a single session
over a frozen, pre-registered list of 16 evaluation rows --- every test access
is logged by the harness before any test data is read. No intermediate test
evaluation and no evaluate-then-decide selection is possible under this
protocol.

\textbf{Test-time adaptation.} On our model only, and pre-registered before
the session, we evaluate AdaBN~\cite{Li-2017} (full-pass re-estimation of
batch-norm statistics on the unlabeled test set), T3A~\cite{Iwasawa-2021} (a
batch variant adjusting the classifier prototypes from confident test
pseudo-labels), and their combination, with all hyperparameters fixed a
priori. These bound how much of the residual gap is recoverable at inference
time. We also evaluate a pre-registered amplitude-scaling augmentation arm
(\emph{C1-aug}) on both rotations, with a declared discriminator between a
cross-domain effect and generic regularization (\secref{sec:res_tta}).
