% !TEX root = template.tex

\section{Related Work}
\label{sec:related_work}

\textbf{WiFi CSI human activity recognition.}
Early CSI HAR pipelines fed hand-crafted statistics of the amplitude/phase
time series to shallow classifiers; the field moved decisively to deep models
operating on time--frequency representations, of which the micro-Doppler
spectrogram is the most common~\cite{Wang-2019}. The reference point for this
report is SHARP~\cite{Meneghello-2023}, which extracts a Doppler representation
from commodity IEEE~802.11 CSI by removing the phase offsets and reconstructing
the channel, and classifies activities with a comparatively shallow, wide
convolutional network followed by a decision-fusion step across antennas. SHARP
reports strong in-environment accuracy but, like most of the literature, its
headline numbers mix training and test environments; the cross-environment
setting, where the geometry at test time is unseen, is where accuracy is known
to degrade and is the setting we adopt. We reproduce the SHARP model as our C0
anchor and reuse its antenna decision-fusion for that configuration, so that our
comparison is anchored to a published, faithful baseline rather than to an
in-house model of unknown strength.

\textbf{Domain generalization by adversarial invariance.}
The dominant recipe for making a representation domain-invariant is adversarial:
a domain discriminator is trained on the encoder features while a gradient
reversal layer (GRL)~\cite{Ganin-2016} inverts its gradient into the encoder, so
that the encoder is optimized to make the domain \emph{unpredictable} while the
task head still classifies. DANN-style training has been transplanted into CSI
sensing to remove environment- and subject-specific nuisance factors. The
implicit precondition, rarely tested, is that the nuisance factor is actually
present and readable in the features; when it is not, the adversary reduces to a
gradient of noise. A central empirical point of this report is to \emph{measure}
that precondition directly on our encoder, rather than assume it, and to show
that the adversary's cost is paid whether or not the target exists.

\textbf{Contrastive representation learning.}
Supervised contrastive learning (SupCon)~\cite{Khosla-2020} extends the
self-supervised InfoNCE objective~\cite{Chen-2020} by treating all same-label
samples as positives, and has been reported to yield representations that are
more robust and transferable than those trained with cross-entropy. It has been
proposed for sensing modalities as a route to environment-robust features. The
promise is geometric --- a class-collapsed, well-separated embedding --- but
whether that geometry survives a linear (or any) readout, and whether it
transfers better than CE across environments, is empirical. We evaluate SupCon
under the identical LOEO protocol and probe its representation with linear,
nearest-class-mean and kNN readouts to test the transferability claim head-on.

\textbf{Test-time adaptation.}
When some unlabeled target data is available at inference, test-time adaptation
can partially close the domain gap without retraining: AdaBN~\cite{Li-2017}
re-estimates batch-normalization statistics on the target distribution, and
T3A~\cite{Iwasawa-2021} adjusts the classifier prototypes from confident target
pseudo-labels. These are complementary to the training-time objectives above,
and we include them as pre-registered rows on our CE model to bound how much
of the residual gap is recoverable purely at test time under our deployment
assumptions.

\textbf{Positioning.}
Prior work overwhelmingly reports where a domain-invariance or contrastive
objective \emph{helped}. Our contribution is orthogonal and, we argue,
complementary: a controlled study, under one shared apparatus and a strict
single-use test protocol, in which both objectives fail on a realistic
CSI benchmark, together with frozen-encoder diagnostics that explain the failure
as structural rather than incidental. Negative results of this kind are
underreported and, on the common class of datasets dominated by one training
environment, directly actionable.
